### 2019-07-19 manuscript/results.tex
- Final ms changes pass-through, mainly spaces, commas, spelling, etc. - Leaving FIXME marks for galley proofs. - Will update archive once more with submission version.

    \item Are conclusions robust to assumptions about hidden state transitions?
    Yes, we found that allowing different types of asymmetry in transitions within and between hidden states did not change our conclusions about net diversification differences.
    Hidden state models with asymmetric rates are, however, strongly preferred over models with equal rates between hidden states (\cref{supptable:asymmetry}), and they show stronger differences between some net diversification rates (\cref{suppfigure:asymmetric}).

>>>>

    \item Are conclusions robust to assumptions about hidden state transitions?
    Yes, we found that allowing different types of asymmetry in transitions within and between hidden states did not change our conclusions about net diversification differences.
    Hidden state models with asymmetric rates are, however, strongly preferred over models with equal rates between hidden states (\cref{supptable:asymmetry}), and they show stronger differences between some net diversification rates (\cref{suppfigure:asymmetric}).
   The effect of the asymmetry of the hidden state transitions is better observed in the ancestral state estimations (\cref{suppfigure:DPnodipABasr,suppfigure:ICABasr,suppfigure:IDCDCPnodipABasr}), which show that moving out of state A (dark colors) happens quickly, with rate $\alpha$,  whereas evolving out of hidden state B (light colors) is slow, with rate $\beta$.
